Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-02-12 Ben_Manuscripts/thesis/transport_si.tex
starting dissertation

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{authblk}

\externaldocument[M-]{Final_Draft}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}
\renewcommand{\thetable}{S\arabic{table}}

\title{Supporting Information: Chemically Selective Transport in a Cross-Linked 
H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author[1]{Benjamin J. Coscia}
\author[1]{Michael R. Shirts} 
\date{E-mail: michael.shirts@colorado.edu}

\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

\begin{document}

  \maketitle
  \graphicspath{{./supporting_figures/}}
  \bibliographystyle{ieeetr}

  \section{Setup and analysis scripts}\label{section:python_scripts}

  All python and bash scripts used to set up systems and conduct post-simulation trajectory
  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  Documentation for the \texttt{LLC\_Membranes} repository is available at 
  \texttt{https://llc-membranes.readthedocs.io/en/latest/}. Table~\ref{table:python_scripts}
  provides more detail about specific scripts used for each type of analysis performed in
  the main text.

@@

  \caption{The first column provides the names of the python scripts available in
  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and 
  post-simulation trajectory analysis. Paths preceding script names are relative to the
  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{table:python_scripts}

@@

  \section{Water content equilibration}\label{section:water_content_equil}

  We initially attempted to equilibrate our system with water by allowing water
  molecules to naturally penetrate the membrane from a water bath separating
  periodic images of the system in the $z$-direction (see Figure~\ref{fig:gap}).
  We allowed a dry, previously equilibrated system to further equilibrate in
  coexistence with a 3 nm-thick (in the $z$-direction) layer of water. Water
  readily enters the tail region where the density of monomers is low. About 3
  times more water molecules occupy the tail region after 1000 ns of
  equilibration (see Figure~\ref{fig:equilibrated_water_penetration}). Although
  the water level in the pore appears to plateau in this system, it is clear that
  equilibration of this system is kinetically limited since water does not fill
  the pores uniformly (see Figure~\ref{fig:penetration_density}). The density of
  water along the pore axis, averaged over the last 50 nanoseconds of simulation,
  is close to zero at the membrane center. Therefore, we required a different
  equilibration technique in order to overcome the kinetic limitation.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.18\textwidth}
  \includegraphics[width=\linewidth]{gap.pdf}
  \caption{}\label{fig:gap}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with : solute_partitioning.py -t shifted.xtc -g berendsen.gro -buffer 2 -r SOL
% in directory : /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/gaps/pre_equilibrated
  \includegraphics[width=\linewidth]{equilibrated_water_penetration.pdf}
  \caption{}\label{fig:equilibrated_water_penetration}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with custom script density.py located in same directory as above.
  \includegraphics[width=\linewidth]{penetration_density.pdf}
  \caption{}\label{fig:penetration_density}
  \end{subfigure}  
  \caption{(a) Using an equilibrated dry configuration, we inserted a 3 nm thick layer 
  of water between periodic copies of the system in the $z$-direction. (b) Water slowly
  enters the membrane. Most water enters the tail region where the density of monomers
  is lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
  content of the pore appears equilibrated in (b), the density of water throughout
  the pores is not uniform, with almost no water close to the pore center. Note that
  the density is not shown below 3 nm or above 9.5 nm, because the the system
  enters the water layer at those points.
  }\label{fig:gap_solvation}
  \end{figure}

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails in addition to a water reservoir between periodic images. We filled
  the pores with water by running \texttt{gmx solvate} on our initial
  configuration and removing any water molecules placed in the tail region. The
  GROMACS command \texttt{gmx solvate} places water molecules in proximity to
  other atoms based on their van der Waals radii and therefore does
  a decent job of preventing equilibration issues. This also means that the
  initial pore radius dictates the water content of the pore. We can however, put
  arbitrary amounts of water into the tail region. We chose to test systems with
  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
  given in Table~\ref{table:water_content}.

  \begin{table}[!htb]
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
  \hline
  5                 &        5.67       &     1.09          \\
  6                 &        2.88       &     2.38          \\
  7                 &        1.91       &     4.12          \\
  8                 &        2.78       &     6.00          \\
  \hline
  \end{tabular}
  \caption{We chose a diverse combination of initial pore and tail water
  contents in order to study its effect on equilibrium water
  content.}\label{table:water_content}
  \end{table}

  Systems appear to be most stable when there is more water in the pores than
  tails. In systems started with more water in the tails
  (Figures~\ref{fig:r5_gap} and \ref{fig:r6_gap}), the pore water content tends
  to increase over time, while that of the tails decreases or stays stable.
  Filling the pores with water is likely a very long process since it requires
  monomers to make space for water molecules. Systems started with a higher pore
  water content (Figures~\ref{fig:r7_gap} and \ref{fig:r8_gap}) tend to plateau
  relatively quickly, with about one third of the water staying in the tails.  We
  used this ratio in order to construct the initial configurations used for the
  studies in the main text.  Clearly, a more complicated methodology is needed in
  order to predict the equilibrium water content of a given LLC membrane.
  However, getting the value exactly right is not required for our study.
  Instead, we can observe mechanisms as a function of water content in each
  region.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated by running: solute_partitioning.py -t stabilized.xtc -g PR.gro -buffer 3 --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/5/1.09_5.67
  \includegraphics[width=\linewidth]{r5_gap.pdf}
  \caption{r = 5~\AA}\label{fig:r5_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g PR.gro -buffer 2.5 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/6/2.38_2.88
  \includegraphics[width=\linewidth]{r6_gap.pdf}
  \caption{r = 6~\AA}\label{fig:r6_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g last.gro -buffer 3 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/6/4.12_1.91
  \includegraphics[width=\linewidth]{r7_gap.pdf}
  \caption{r = 7~\AA}\label{fig:r7_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g last.gro -buffer 3 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/8/6.00_2.78
  \includegraphics[width=\linewidth]{r8_gap.pdf}
  \caption{r = 8~\AA}\label{fig:r8_gap}
  \end{subfigure}
  \caption{There is likely more water in the pore region than in the tail region.
  When we create configurations with more water in the tails, equilibration is 
  slow. When configurations start with more water in the pores, the water content
  in each region equilibrates quickly.}\label{fig:gap_prefilled_equil}
  \end{figure}

  Since the equilibrium water content is unclear based on the previous
  simulations, we elected to choose and study systems with two different water
  contents. We removed the water reservoir and allowed the pore and tail water
  contents to equilibrate with 5 and 10 wt \% total water. We placed one third of
  the total water needed in the tails, based on the intuition gained in
  Figure~\ref{fig:gap_prefilled_equil}. We considered the water content
  equilibrated once the water contents plateaued. The 5 wt\% system did
  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
  while the 10 wt \% water system equilibrated within the first 100 ns of 
  simulation (Figure~\ref{fig:10wt_offset_equil}).
  The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
  systems respectively.
  \clearpage
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{5 wt \%}\label{fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{10 wt \%}\label{fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{fig:solvation_equilibration}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
  \end{subfigure}
  \caption{The water content in the tail and pore region is not affected
  by cross-linking}\label{fig:xlinked_solvation_equilibration}
  \end{figure}

  \clearpage
  \section{Solute Interaction}\label{section:solute_interaction}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
  \caption{Interactions between same-solutes are negligible when systems are 
  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
  molecules the most, does so less than 0.05 \% of the time.}\label{fig:solute_interaction}
  \end{figure}

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{fig:se_intersection_sensitivity}
%  \end{figure}

  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}

  We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
  not have a significant influence on the ranking of the solute MSDs (see 
  Figure~\ref{fig:lag_sensitivity}). Although there is minor re-ranking among solutes
  with similar MSDs, it does not affect any of the conclusions drawn in the main text.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_2.pdf}
  \caption{Time lag = 200 ns}\label{fig:F0.2}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_3.pdf}
  \caption{Time lag = 300 ns}\label{fig:F0.3}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_4.pdf}
  \caption{Time lag = 400 ns}\label{fig:F0.4}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_5.pdf}
  \caption{Time lag = 500 ns}\label{fig:F0.5}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_6.pdf}
  \caption{Time lag = 600 ns}\label{fig:F0.6}
  \end{subfigure}
  \caption{The choice of time lag used to report solute MSDs does not 
  influence the trends reported in the main text. We observe minor re-ranking
  of solutes with similar MSDs and note that longer time lags generally
  lead to large error bars on the MSDs, as expected. }\label{fig:lag_sensitivity}
  \end{figure}

@@

  \section{Pore Region Definition}\label{section:pore-region}

  We performed a sensitivity analysis in order to determine the radial 
  cut-off that maximizes the difference in hop lengths in and out of 
  the pore region. We varied the location of the cut-off defining the
  edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
  varied the cut-off in increments of 0.01 from 0.7 to 0.8 in order to
  increase our resolution about the maximum (see Figure~\ref{fig:pore_cutoff}). 
  Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore.

  \begin{figure}[H]
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{fig:pore_cutoff}
  \end{figure}

  \clearpage
  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \centering
  \includegraphics[trim={0 0.5cm 0.5cm 0.5cm}, clip, width=0.5\textwidth]{hbond_sensitivity_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{hbond_sensitivity.pdf}
  \end{subfigure}
  \caption{We tested the sensitivity of our hydrogen bond detection to the chosen 
  geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{fig:hbond_sensitivity}
  \end{figure}

>>>>

chapter{Supporting Information to Chapter 3}\label{SI:ch3}

  \section{Setup and analysis scripts}\label{S-section:python_scripts_transport}

  All python and bash scripts used to set up systems and conduct post-simulation trajectory
  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  Documentation for the \texttt{LLC\_Membranes} repository is available at 
  \texttt{https://llc-membranes.readthedocs.io/en/latest/}. Table~\ref{S-table:python_scripts_transport}
  provides more detail about specific scripts used for each type of analysis performed in
  the main text.

@@

  \caption{The first column provides the names of the python scripts available in
  the \texttt{LLC\_Membranes} GitHub repository that were used for system setup and 
  post-simulation trajectory analysis. Paths preceding script names are relative to the
  \texttt{LLC\_Membranes/LLC\_Membranes} directory. The second columns lists the section in the main
  text where the output or usage of the script is first described. The third column
  gives a brief description of the purpose of each script.
  }~\label{S-table:python_scripts_transport}

@@

  \section{Water content equilibration}\label{S-section:water_content_equil}

  We initially attempted to equilibrate our system with water by allowing water
  molecules to naturally penetrate the membrane from a water bath separating
  periodic images of the system in the $z$-direction (see Figure~\ref{S-fig:gap}).
  We allowed a dry, previously equilibrated system to further equilibrate in
  coexistence with a 3 nm-thick (in the $z$-direction) layer of water. Water
  readily enters the tail region where the density of monomers is low. About 3
  times more water molecules occupy the tail region after 1000 ns of
  equilibration (see Figure~\ref{S-fig:equilibrated_water_penetration}). Although
  the water level in the pore appears to plateau in this system, it is clear that
  equilibration of this system is kinetically limited since water does not fill
  the pores uniformly (see Figure~\ref{S-fig:penetration_density}). The density of
  water along the pore axis, averaged over the last 50 nanoseconds of simulation,
  is close to zero at the membrane center. Therefore, we required a different
  equilibration technique in order to overcome the kinetic limitation.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.18\textwidth}
  \includegraphics[width=\linewidth]{gap.pdf}
  \caption{}\label{S-fig:gap}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with : solute_partitioning.py -t shifted.xtc -g berendsen.gro -buffer 2 -r SOL
% in directory : /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/gaps/pre_equilibrated
  \includegraphics[width=\linewidth]{equilibrated_water_penetration.pdf}
  \caption{}\label{S-fig:equilibrated_water_penetration}
  \end{subfigure}  
  \begin{subfigure}{0.37\textwidth}
% Generated with custom script density.py located in same directory as above.
  \includegraphics[width=\linewidth]{penetration_density.pdf}
  \caption{}\label{S-fig:penetration_density}
  \end{subfigure}  
  \caption{(a) Using an equilibrated dry configuration, we inserted a 3 nm thick layer 
  of water between periodic copies of the system in the $z$-direction. (b) Water slowly
  enters the membrane. Most water enters the tail region where the density of monomers
  is lowest. Water entering the pore plateaus after 500 ns. (c) Although the water
  content of the pore appears equilibrated in (b), the density of water throughout
  the pores is not uniform, with almost no water close to the pore center. Note that
  the density is not shown below 3 nm or above 9.5 nm, because the the system
  enters the water layer at those points.
  }\label{S-fig:gap_solvation}
  \end{figure}

  We equilibrated 4 systems where we initially placed water in the pores and in
  the tails in addition to a water reservoir between periodic images. We filled
  the pores with water by running \texttt{gmx solvate} on our initial
  configuration and removing any water molecules placed in the tail region. The
  GROMACS command \texttt{gmx solvate} places water molecules in proximity to
  other atoms based on their van der Waals radii and therefore does
  a decent job of preventing equilibration issues. This also means that the
  initial pore radius dictates the water content of the pore. We can however, put
  arbitrary amounts of water into the tail region. We chose to test systems with
  initial pore radii of 5, 6, 7 and 8 \AA~with tail and pore water compositions
  given in Table~\ref{S-table:water_content}.

  \begin{table}[!htb]
  \centering
  \begin{tabular}{|c|c|c|}
  \hline
  Pore Radius (\AA) & wt \% water tails & wt \% water pores \\
  \hline
  5                 &        5.67       &     1.09          \\
  6                 &        2.88       &     2.38          \\
  7                 &        1.91       &     4.12          \\
  8                 &        2.78       &     6.00          \\
  \hline
  \end{tabular}
  \caption{We chose a diverse combination of initial pore and tail water
  contents in order to study its effect on equilibrium water
  content.}\label{S-table:water_content}
  \end{table}

  Systems appear to be most stable when there is more water in the pores than
  tails. In systems started with more water in the tails
  (Figures~\ref{S-fig:r5_gap} and \ref{S-fig:r6_gap}), the pore water content tends
  to increase over time, while that of the tails decreases or stays stable.
  Filling the pores with water is likely a very long process since it requires
  monomers to make space for water molecules. Systems started with a higher pore
  water content (Figures~\ref{S-fig:r7_gap} and \ref{S-fig:r8_gap}) tend to plateau
  relatively quickly, with about one third of the water staying in the tails.  We
  used this ratio in order to construct the initial configurations used for the
  studies in the main text.  Clearly, a more complicated methodology is needed in
  order to predict the equilibrium water content of a given LLC membrane.
  However, getting the value exactly right is not required for our study.
  Instead, we can observe mechanisms as a function of water content in each
  region.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated by running: solute_partitioning.py -t stabilized.xtc -g PR.gro -buffer 3 --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/5/1.09_5.67
  \includegraphics[width=\linewidth]{r5_gap.pdf}
  \caption{r = 5~\AA}\label{S-fig:r5_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g PR.gro -buffer 2.5 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/6/2.38_2.88
  \includegraphics[width=\linewidth]{r6_gap.pdf}
  \caption{r = 6~\AA}\label{S-fig:r6_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g last.gro -buffer 3 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/6/4.12_1.91
  \includegraphics[width=\linewidth]{r7_gap.pdf}
  \caption{r = 7~\AA}\label{S-fig:r7_gap}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
% Generate by running: solute_partitioning.py -t stabilized.xtc -g last.gro -buffer 3 -r SOL --savename water_partition.pl
% In directory: /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/water_content_experiments/8/6.00_2.78
  \includegraphics[width=\linewidth]{r8_gap.pdf}
  \caption{r = 8~\AA}\label{S-fig:r8_gap}
  \end{subfigure}
  \caption{There is likely more water in the pore region than in the tail region.
  When we create configurations with more water in the tails, equilibration is 
  slow. When configurations start with more water in the pores, the water content
  in each region equilibrates quickly.}\label{S-fig:gap_prefilled_equil}
  \end{figure}

  Since the equilibrium water content is unclear based on the previous
  simulations, we elected to choose and study systems with two different water
  contents. We removed the water reservoir and allowed the pore and tail water
  contents to equilibrate with 5 and 10 wt \% total water. We placed one third of
  the total water needed in the tails, based on the intuition gained in
  Figure~\ref{S-fig:gap_prefilled_equil}. We considered the water content
  equilibrated once the water contents plateaued. The 5 wt\% system did
  not plateau until $\sim$ 600 ns (Figure~\ref{S-fig:5wt_offset_equil})
  while the 10 wt \% water system equilibrated within the first 100 ns of 
  simulation (Figure~\ref{S-fig:10wt_offset_equil}).
  The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
  systems respectively.
  \clearpage
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{5 wt \%}\label{S-fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{10 wt \%}\label{S-fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{S-fig:solvation_equilibration}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
  \caption{5 wt\%}\label{S-fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{10 wt\%}\label{S-fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
  \end{subfigure}
  \caption{The water content in the tail and pore region is not affected
  by cross-linking}\label{S-fig:xlinked_solvation_equilibration}
  \end{figure}

  \clearpage
  \section{Solute Interaction}\label{S-section:solute_interaction}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{solute_interaction.pdf}
  \caption{Interactions between same-solutes are negligible when systems are 
  built with 6 solutes per pore. Even methanol, which interacts with other same-solute
  molecules the most, does so less than 0.05 \% of the time.}\label{S-fig:solute_interaction}
  \end{figure}

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{S-section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{S-fig:se_intersection_sensitivity}
%  \end{figure}

  \section{Solute MSD Ranking Time Lag Sensitivity}\label{S-section:lag_sensitivity}

  We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
  not have a significant influence on the ranking of the solute MSDs (see 
  Figure~\ref{S-fig:lag_sensitivity}). Although there is minor re-ranking among solutes
  with similar MSDs, it does not affect any of the conclusions drawn in the main text.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_2.pdf}
  \caption{Time lag = 200 ns}\label{S-fig:F0.2}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_3.pdf}
  \caption{Time lag = 300 ns}\label{S-fig:F0.3}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_4.pdf}
  \caption{Time lag = 400 ns}\label{S-fig:F0.4}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_5.pdf}
  \caption{Time lag = 500 ns}\label{S-fig:F0.5}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_6.pdf}
  \caption{Time lag = 600 ns}\label{S-fig:F0.6}
  \end{subfigure}
  \caption{The choice of time lag used to report solute MSDs does not 
  influence the trends reported in the main text. We observe minor re-ranking
  of solutes with similar MSDs and note that longer time lags generally
  lead to large error bars on the MSDs, as expected. }\label{S-fig:lag_sensitivity}
  \end{figure}

@@

  \section{Pore Region Definition}\label{S-section:pore-region}

  We performed a sensitivity analysis in order to determine the radial 
  cut-off that maximizes the difference in hop lengths in and out of 
  the pore region. We varied the location of the cut-off defining the
  edge of the pore region in increments of 0.05 from 0.3 to 0.7. We
  varied the cut-off in increments of 0.01 from 0.7 to 0.8 in order to
  increase our resolution about the maximum (see Figure~\ref{S-fig:pore_cutoff}). 
  Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore.

  \begin{figure}[!h]
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{S-fig:pore_cutoff}
  \end{figure}

  \clearpage
  \section{Hydrogen Bond Detection Sensitivity}\label{S-section:hbond_sensitivity}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  \centering
  \includegraphics[trim={0 0.5cm 0.5cm 0.5cm}, clip, width=0.5\textwidth]{hbond_sensitivity_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{hbond_sensitivity.pdf}
  \end{subfigure}
  \caption{We tested the sensitivity of our hydrogen bond detection to the chosen 
  geometric criteria for hydrogen bonding. We varied the distance cut-off between 3.0 and
  4.0 \AA, and varied the angle cut-off between 25 and 35 \degree.}\label{S-fig:hbond_sensitivity}
  \end{figure}

  We tested the sensitivity of this criteria to ensure that our conclusions
  were not a strong function of the chosen criteria. In Figure~\ref{S-fig:hbond_sensitivity} we
  plotted the results of the same calculation performed to create Figure~\ref{fig:multi_hbonds}c.
  We varied the distance cut-off between 3.0 and 4.0 \AA, and varied the
  angle cut-off between 25 and 35 \degree.
